An asymptotically normal out-of-sample test of equal predictive accuracy for nested models

### 2014-10-31 mixedwindow.tex
Add variance-covariance matrix to Theorem 1

\begin{thm}\label{res:1}
  Suppose that Assumptions~\ref{a1} -- \ref{a4} hold.  Then $\sqrt{P}
  (\fb - \E f_t) \to^d N(0, \Sigma)$.
\end{thm}

>>>>

Asymptotic normality of the OOS average follows directly from the
previous three assumptions without any other conditions. The proof is
presented in the Appendix and follows \citet{Wes:96} directly.

\begin{thm}\label{res:1}
  If Assumptions~\ref{a1} -- \ref{a4} hold then $\sqrt{P} (\fb - \E
  \fb(\btrue)) \to^d N(0, \Sigma)$, with
  \begin{align*}
    \Sigma &= S_{ff} + S_{fg} + S_{fg}' + 2 \, S_{gg}, &
    S_{ff}  &= \lim P \var(\fb(\btrue)), \\
    S_{fg}  &= \lim P \cov(\fb(\btrue), \gb(\btrue)), &
    S_{gg}  &= \lim P \var(\gb(\btrue)).
  \end{align*}
\end{thm}

Null hypothesis: $y_{t+1} - x_t'\beta_0$ is an MDS with respect to
\begin{equation*}
  \Fs = \sigma((x_t, y_t, z_t), (x_{t-1}, y_{t-1}, z_{t-1}), \dots).
\end{equation*}

Clearly, the main use of this theorem is to test the null hypothesis
$\E f_t = 0$.
